### 2023-09-06 Manuscript/Draft2.Rmd
manuscipt update

Tables \@ref(tab:YTresultsallstrata), \@ref(tab:YTresultsreducedstrata), \@ref(tab:CodERROR), and \@ref(tab:HadERROR) contain the absolute error between biomass estimates and model output for each of our 20-year biomass estimates. While the model-based results provided a slightly lower overall mean absolute error (0.34) compared to the stratified mean (0.38), the variance of all VAST absolute errors (0.10) was much larger than the stratified mean (0.02). When considering individual scenarios, while about $96\%$ had a VAST estimate with a lower absolute error than the corresponding stratified mean estimate, $63\%$ of individual scenarios contained a VAST estimate with a worse error than the corresponding stratified mean estimate. VAST models that included covariate information provided the lowest overall absolute errors and standard deviations. Models with covariates had an average absolute error of 0.22, compared to models that did not include covariate information having an average error of 0.46, and stratified mean estimates produces an average error of 0.39. These findings demonstrate the ability of spatio-temporal models to account for spatial variation in the species being sampled under the right conditions, but also highlight volatility/sensitivity of model estimates to the settings being used and/or the covariate response detected in the data.

>>>>

Tables \@ref(tab:YTresultsallstrata), \@ref(tab:YTresultsreducedstrata), \@ref(tab:CodERROR), and \@ref(tab:HadERROR) contain the absolute error between biomass estimates and model output for each of our 20-year biomass estimates. While the model-based results provided a slightly lower overall mean absolute error (0.34) compared to the stratified mean (0.38), the variance of all VAST absolute errors (0.10) was much larger than the stratified mean (0.02). The difference in variance is further illustrated by the median error values, with model-based estimates resulting in a median value of 0.235 while stratified mean values had a median error of 0.34. When considering individual scenarios, while about $96\%$ had a VAST estimate with a lower absolute error than the corresponding stratified mean estimate, $63\%$ of individual scenarios contained a VAST estimate with a worse error than the corresponding stratified mean estimate. VAST models that included covariate information provided the lowest overall absolute errors and standard deviations. Models with covariates had an average absolute error of 0.22 (median 0.19), compared to models that did not include covariate information having an average error of 0.46 (median 0.31), and stratified mean estimates produced an average error of 0.38 (median 0.34). These findings demonstrate the ability of spatio-temporal models to account for spatial variation in the species being sampled under the right conditions, but also highlight volatility/sensitivity of model estimates to the settings being used and/or the covariate response detected in the data.
